%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Adapted By : Ivy Bixler
% A License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeBullet}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ivy Bixler} & Email: \href{mailto:ivybixler@gmail.com}{ivybixler@gmail.com} \\
  Worcester, MA & Mobile: (919) 771-9270 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Worcester Polytechnic Institute (WPI)}{Worcester, MA}
    {B.S. in Computer Science}{Aug 2021 -- May 2025}
    \resumeItemListStart
      \resumeBullet{Completed Interactive Qualifying Project in Glacier National Park (Aug--Oct 2023).}
      \resumeBullet{Coursework: Algorithms, Operating Systems, Database Systems, Computer Networks, Artificial Intelligence, Data Mining, Programming Languages.}
      \resumeBullet{Assisted faculty by writing a setup guide for emulating the x86-64 architecture.}
      \resumeBullet{Proposed a capstone project creating interactive music-based collages from user listening data.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: Java, C/C++, Python, SQL, JavaScript}
  }
  \item{
    \textbf{Web \& Databases}{: HTML, CSS, MongoDB, PostgreSQL}
  }
  \item{
    \textbf{Tools \& Platforms}{: Git, Docker, Linux, MacOS, QEMU, GitHub CI}
  }
  \item{
    \textbf{Networking}{: Computer Networks, Packet Analysis, Routing, Firewalls}
  }
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{Tile.Music}
    {Built a fully Dockerized microservice architecture to collect and analyze user listening data. Reduced Spotify API calls by a factor of 300. Generates interactive collages reflecting users’ listening habits using a scheduled job system.}

  \resumeSubItem{Bus Lateness Estimator}
    {Implemented a job scheduler to determine arrival times of WRTA buses. Developed an interactive map displaying average lateness per stop.}

  \resumeSubItem{Packet Analysis Program}
    {Analyzed network packet capture files to generate detailed packet summaries and protocol-level insights.}

  \resumeSubItem{Interactive Computer Network Gaming Activity}
    {Configured custom DHCP and Samba servers on Ubuntu 24.04. Demonstrated how Ethernet networking concepts relate to graph theory through hands-on activities.}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Mosaiq Software}{Worcester, MA}
    {Software Engineer}{Nov 2025 -- Present}
    \resumeItemListStart
      \resumeBullet{Designed and implemented a fully RESTful backend for Timlyr, a modern scheduling application inspired by When2Meet.}
      \resumeBullet{Developed API endpoints to aggregate and normalize availability data across multiple users.}
      \resumeBullet{Implemented validation, structured error handling, and consistent resource-based routing to ensure API reliability.}
      \resumeBullet{Collaborated with frontend developers to define API contracts and support a responsive, modern UI.}
      \resumeBullet{Contributed minor frontend features and UI refinements to improve usability and overall user experience.}
    \resumeItemListEnd
  \resumeSubheading
    {BDS Connected Solutions}{Framingham, MA}
    {Break/Fix Technician}{July 2025 -- December 2025}
    \resumeItemListStart
      \resumeBullet{Diagnose and resolve hardware and software issues for demo devices including phones, PCs, tablets, and laptops.}
      \resumeBullet{Apply creative problem-solving to ensure full functionality and adherence to deployment standards.}
      \resumeBullet{Merchandise products according to planograms and store specifications.}
    \resumeItemListEnd

  \resumeSubheading
    {Girls Talk Math at WPI}{Worcester, MA}
    {Team Leader}{Jul 2023 -- Aug 2023 \quad Jul 2024 -- Aug 2024}
    \resumeItemListStart
      \resumeBullet{Taught graph theory concepts through Python to high school students.}
      \resumeBullet{Ensured a safe, inclusive, and supportive learning environment.}
      \resumeBullet{Increased camper engagement tenfold by integrating an interactive computer networking activity.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}
